Equalizer\\Programming and User Guide

### 2012-01-27 Developer/ProgrammingGuide/paper.tex
Minor fix

In immersive visualization, the observer is tracked in and the view
frusta are adapted to the viewer's position and orientation, as shown
in \fig{fTracked}. The transformation $origin \rightarrow viewer$ is set by
the application using \textsf{Config::setHead\-Matrix}, which is used by
the server to compute the eye positions, and consequently the view frusta.

>>>>

In immersive visualization, the observer is tracked in and the view
frusta are adapted to the viewer's position and orientation, as shown
in \fig{fTracked}. The transformation $origin \rightarrow viewer$ is set by
the application using \textsf{Observer::setHead\-Matrix}, which is used by
the server to compute the eye positions, and consequently the view frusta.
